\tool: Revisiting BadUSB with Type-C

### 2021-03-27 WOOT/BadUSBC.tex
JFA
Add author, minor changes

\author{Anonymous Authors}
%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%}

@@

\newacro{USB}{Universal Serial Bus}
\newacro{HID}{Human Interface Device}
\newacro{UI}{User Interface}
\newacro{PnP}{Plug-and-Play}
\newacro{OEM}{Original Equipment Manufacturer}
\newacro{DoS}{Denial of Service}
\newacro{MHL}{Mobile High-Definition Link}
\newacro{URB}{USB Request Block}
\newacro{OCR}{Optical Character Recognition}
\newacro{GUI}{Graphical User Interface}

>>>>

\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1}\orcidA{}, Yechang Wu\textsuperscript{1}, Shuqing Li\textsuperscript{1}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2}}
\IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\
		\textsuperscript{2}\textit{Research Institute of Trustworthy Autonomous Systems, Southern University of Science and Technology} \\
	\{11712009,11711918,lisq2017,11711809,11712021\}@mail.sustech.edu.cn,zhangfw@sustech.edu.cn\\
}
}

@@

\newacro{USB}{Universal Serial Bus}
\newacro{HID}{Human Interface Device}
\newacro{UI}{User Interface}
\newacro{PnP}{Plug-and-Play}
\newacro{OEM}{Original Equipment Manufacturer}
\newacro{DoS}{Denial of Service}
\newacro{MHL}{Mobile High-Definition Link}
\newacro{URB}{USB Request Block}
\newacro{OCR}{Optical Character Recognition}
\newacro{GUI}{Graphical User Interface}
\newacro{JFA}{Juice Filming Attacks}
